密文重复数据删除机制的频率攻击方法

### 2018-12-28 paper/Conclusion.tex
ING | complete chapter 4 and begin chapter 5 before workflow

@@

% types of files are especially insecure under these attacks.    
% We propose two new inference attacks, which augment the prior attack \cite{li17} with high precision inference and relaxed adversarial knowledge, respectively.   
% While prior work \cite{li17} has illustrated the vulnerability  via frequency analysis, this paper presents an in-depth study on the security of encrypted deduplication, and       
 We pose three directions for future work. First, we consider a complete old backup as the auxiliary information, and do not study how to launch attack if the adversary only has partial knowledge about the old backup. Possibly, we can still apply the frequency analysis attacks to extract characteristics from the available partial backup, and infer ciphertext-plaintext pairs by comparing the characteristics with those in the target backup. One direction is can we design advanced inference attacks, which  perform better than directly applying our attacks in this partial knowledge case?

 % The attack effectiveness depends on how the information in the partial backup correlates with the target backup.       
 Second, we adjust the parameters of the frequency analysis attacks based on their effectiveness, which can only be learnt after the attacks have happened. We do not study how to derive the optimal parameters from auxiliary information beforehand. Future work may do better.

 % We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently.

 % the frequency analysis attacks are parameter sensitive. We adjust parameters based on the attack effectiveness (that can only be measured after the attack happens), and do not study how to identify the optimal parameter configuration  beforehand. We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently. Future work may do better.

 % our proposed attacks are parameter sensitive. In evaluation, we adjust the parameters based on attack results, and report the security vulnerability of encrypted deduplication under some {\em specific} parameter settings of our attacks. We do not  study how to identify the optimal parameter setting of attack without the knowledge of attack results. We begin to consider that the attack configurations possibly depend on the characteristics of target workloads, but do not see how to derive them. Future work may do better.

% help practitioners and researchers better understand the security issues in encrypted deduplication storage and motivate more research along this direction.
% While 
% of encrypted deduplication
% Although it is vulnerable to frequency analysis, prior work \cite{li17} shows that classical frequency analysis can only infer a few original chunks in practice. This paper considers to increase the effectiveness of frequency analysis with additional leakages. Specifically, we present three new inference attacks by exploiting the size and order leakages that have been witnessed in deduplication systems \cite{xia11,lillibridge09,zhu08,douceur02, wilcox-ohearn08, bellare13b}. We evaluate the effectiveness of  our attacks with real-world datasets, and show that they can infer significant amount of original data under different types of workloads. We also discuss possible countermeasures to address the leakage channels exploited by our attacks. We pose the following future works.

@@

% - Our attacks are parameter sensitive. One direction is to explore the relationship between configuration and workload characteristics.

% - There seems a tradeoff between size-based attack and distribution-based attack. Throughout our experiment, size-based attack operates big chunks better, since they have more variances on chunk size. The distribution-based attack is expected to operate small chunks better, because there exists more chunk locality between small chunks.

% - To defend our attacks, one approach is to obfuscate the chunk distributions. A recent work suggests to add redundant chunks to mix up network traffic. It works for changing chunk distribution, but depends on knowing if a chunk is duplicate before deduplication.

% - This paper aims to report the vulnerabilities of encrypted deduplication, while not target on implementing a real attack against practical encrypted deduplication systems. Another direction is deploy our attack design in practice to alert the vulerabilities of encrypted deduplication.

>>>>

加密重复数据删除应用确定性加密，并由此泄漏了明文的频率。本文重新审视了频率分析引起的安全漏洞，并证明加密重复数据删除更容易受到推理攻击。本文提出了两种新的频率分析攻击方法，它们在攻击者所具有的条件的不同假设下都能实现高推理率和高推理精度。本文用三个真实世界的数据集来验证评估这两种攻击方法，提出关于其性质的各种新观察，并进一步分析它们如何带来实际损害。本文还讨论了可能的对策的优缺点，以建议从业者安全地实施和部署加密的重复数据删除存储系统。

@@

\section{后续工作}

我们为未来的工作提出三个方向。
 
 首先，我们将完整的旧备份视为辅助信息，如果攻击者仅对旧备份有部分了解，则不研究如何发起攻击。可能的是，我们仍然可以应用频率分析攻击从可用的部分备份中提取特征，并通过比较特征与目标备份中的特征来推断密文 - 明文对。一个方向是我们可以设计先进的推理攻击，这比在这个部分知识案例中直接应用我们的攻击更好吗？
      
 其次，我们根据频率分析攻击的有效性调整频率分析攻击的参数，只有在攻击发生后才能学习。我们不研究如何预先从辅助信息中推导出最佳参数。未来的工作可能会做得更好

第三，我们不对实际加密的重复数据删除存储系统实施攻击原型。另一个方向是部署我们的攻击设计和报告加密重复数据删除在实践中的漏洞。

 We pose three directions for future work.

 First, we consider a complete old backup as the auxiliary information, and do not study how to launch attack if the adversary only has partial knowledge about the old backup. Possibly, we can still apply the frequency analysis attacks to extract characteristics from the available partial backup, and infer ciphertext-plaintext pairs by comparing the characteristics with those in the target backup. One direction is can we design advanced inference attacks, which  perform better than directly applying our attacks in this partial knowledge case?

 Second, we adjust the parameters of the frequency analysis attacks based on their effectiveness, which can only be learnt after the attacks have happened. We do not study how to derive the optimal parameters from auxiliary information beforehand. Future work may do better.

@@

### 2018-12-28 paper/background.tex
ING | complete chapter 4 and begin chapter 5 before workflow

具体地，重复数据删除系统首先通过文件切块过程将客户端的文件（例如，备份文件）分割成逻辑数据块，根据每一个逻辑数据块的内容使用HASH算法（散列算法）计算得到其对应的唯一标签（又成为指纹）。如果两个数据块具有相同的标签，那么认为两个数据块相同（不同逻辑数据块计算得到相同的标志的概率忽略不计\citing{black2006compare}），即数据块内容和其标志完全一致；若两个逻辑数据块标签不一致，显然两逻辑数据块不同。重复数据删除系统的存储系统仅存储相同逻辑数据块的副本（称为物理数据块），并且每个相同的逻辑数据块通过一个较小空间开销的索引引用相同的物理数据块。

@@

MLE可以实现为不同的实例化（参见章节：\ref{sec:RelatedWork}）。其中最受欢迎的是融合加密（CE）\citing{douceur2002reclaiming}，它已经在各种存储系统中实现\citing{adya2002farsite,ElephantDrive,MEGA,GNUP2P,Freenet,Cryptosphere,cox2002pastiche,storer2008secure,anderson2010fast}。 CE的主要思想是根据每个明文数据块的内容通过HASH函数（散列函数）导出其对应的MLE密钥。这种方法可以确保具有相同内容的逻辑数据块加密得到的密文数据块始终一致，即可使用密文数据块的标签进行重复数据删除。但也存在部分MLE实例\citing{bellare2013message}允许将相同的明文加密成不同的密文。当然，他们确保用于重复数据删除的标签仍然来自明文，因此他们依然可以通过检查标签的相同性来执行重复数据删除。

>>>>

具体地，重复数据删除系统首先通过文件切块过程将客户端的文件（例如，备份文件）分割成逻辑数据块，根据每一个逻辑数据块的内容使用HASH算法（哈希算法）计算得到其对应的唯一标签（又成为指纹）。如果两个数据块具有相同的标签，那么认为两个数据块相同（不同逻辑数据块计算得到相同的标志的概率忽略不计\citing{black2006compare}），即数据块内容和其标志完全一致；若两个逻辑数据块标签不一致，显然两逻辑数据块不同。重复数据删除系统的存储系统仅存储相同逻辑数据块的副本（称为物理数据块），并且每个相同的逻辑数据块通过一个较小空间开销的索引引用相同的物理数据块。

@@

MLE可以实现为不同的实例化（参见章节：\ref{sec:RelatedWork}）。其中最受欢迎的是融合加密（CE）\citing{douceur2002reclaiming}，它已经在各种存储系统中实现\citing{adya2002farsite,ElephantDrive,MEGA,GNUP2P,Freenet,Cryptosphere,cox2002pastiche,storer2008secure,anderson2010fast}。 CE的主要思想是根据每个明文数据块的内容通过HASH函数（哈希函数）导出其对应的MLE密钥。这种方法可以确保具有相同内容的逻辑数据块加密得到的密文数据块始终一致，即可使用密文数据块的标签进行重复数据删除。但也存在部分MLE实例\citing{bellare2013message}允许将相同的明文加密成不同的密文。当然，他们确保用于重复数据删除的标签仍然来自明文，因此他们依然可以通过检查标签的相同性来执行重复数据删除。

### 2018-12-28 paper/introduction.tex
ING | complete chapter 4 and begin chapter 5 before workflow

为了保护数据隐私，加密重复数据删除（encrypted deduplication）增加了一层作用于逻辑数据块的加密操作。如图\ref{fig:加密重复数据删除系统逻辑视图}所示，该加密层基于数据内容来产生加密密钥\citing{bellare2013message}（例如将数据块的散列值作为密钥\citing{douceur2002reclaiming}），从而将相同的明文数据块加密为相同的密文数据块。系统计算每个密文数据块的散列值(称为指纹，fingerprint)，查询指纹索引（fingerprint index）确定该数据块是否已经存储，最后保存仅具有唯一指纹的密文数据块。需要指出的是，部分加密重复数据删除方案\citing{bellare2013message}采用随机加密算法，但基于明文数据块产生指纹，因此仍然可以通过检查指纹来识别重复数据。

@@

消息锁定加密（message-locked encryption，MLE）确立了加密重复数据删除的密码学基础\citing{bellare2013message}:基于数据内容产生密钥(称为 MLE 密钥)，从而将相同明文加密为相同密文。最流行的MLE实例是收敛加密（convergent encryption，CE）\citing{douceur2002reclaiming}，它使用明文的散列值作为MLE密钥，并基于密文散列值计算指纹，以识别重复数据（如图\ref{fig:加密重复数据删除系统逻辑视图}）。基于CE的加密重复数据删除方案还包括:

\begin{enumerate}
    \item 散列收敛加密（hash convergent encryption，HCE）\citing{douceur2002reclaiming}与CE具有相同的MLE密钥产生规则，但基于明文散列值计算指纹。
    \item 随机收敛加密（random convergent encryption，RCE）\citing{douceur2002reclaiming}使用随机密钥加密以产生非确定的密文，同时也基于明文散列值来进行重复检查。
    \item 收敛扩散（convergent dispersal，CD）\citing{li2016cdstore}使用明文散列值作为秘密共享（secret sharing）的输入种子，在兼容重复数据删除的基础上 提高了密文存储的可靠性。
\end{enumerate}

>>>>

为了保护数据隐私，加密重复数据删除（encrypted deduplication）增加了一层作用于逻辑数据块的加密操作。如图\ref{fig:加密重复数据删除系统逻辑视图}所示，该加密层基于数据内容来产生加密密钥\citing{bellare2013message}（例如将数据块的哈希值作为密钥\citing{douceur2002reclaiming}），从而将相同的明文数据块加密为相同的密文数据块。系统计算每个密文数据块的哈希值(称为指纹，fingerprint)，查询指纹索引（fingerprint index）确定该数据块是否已经存储，最后保存仅具有唯一指纹的密文数据块。需要指出的是，部分加密重复数据删除方案\citing{bellare2013message}采用随机加密算法，但基于明文数据块产生指纹，因此仍然可以通过检查指纹来识别重复数据。

@@

消息锁定加密（message-locked encryption，MLE）确立了加密重复数据删除的密码学基础\citing{bellare2013message}:基于数据内容产生密钥(称为 MLE 密钥)，从而将相同明文加密为相同密文。最流行的MLE实例是收敛加密（convergent encryption，CE）\citing{douceur2002reclaiming}，它使用明文的哈希值作为MLE密钥，并基于密文哈希值计算指纹，以识别重复数据（如图\ref{fig:加密重复数据删除系统逻辑视图}）。基于CE的加密重复数据删除方案还包括:

\begin{enumerate}
    \item 哈希收敛加密（hash convergent encryption，HCE）\citing{douceur2002reclaiming}与CE具有相同的MLE密钥产生规则，但基于明文哈希值计算指纹。
    \item 随机收敛加密（random convergent encryption，RCE）\citing{douceur2002reclaiming}使用随机密钥加密以产生非确定的密文，同时也基于明文哈希值来进行重复检查。
    \item 收敛扩散（convergent dispersal，CD）\citing{li2016cdstore}使用明文哈希值作为秘密共享（secret sharing）的输入种子，在兼容重复数据删除的基础上 提高了密文存储的可靠性。
\end{enumerate}
